### 2019-02-04 thesis_report/introduction.tex
Majorana's -> Majoranas

\comment{It is still an open question what the implementation for a qubit will be, but majorana's are one of the contenders}
	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, the binary unit of information, has been constantly changing.
	For the earliest computers, complex electromechanical systems with gears and cogs fulfilled this role.
	Soon after, binary states were implemented in the form of vacuum tubes, and nowadays it is the transistor which acts as the basic unit of computation.
	Similarly, because quantum computing is still in its infancy, there are still many contenders for what the underlying technology will be: what physical system will form the basis for the quantum bit, the qubit?
	The platforms which are currently explored for the implementation of a qubit include the transmon qubit~\cite{wendin_quantum_2017}, NV-centers~\cite{childress_diamond_2013}, quantum dots~\cite{kloeffel_prospects_2013}, and Majorana bound states~\cite{wendin_quantum_2017}.
	The main problem with most of the quantum computing platforms is that it is very difficult to keep the qubit from decohering.
	To counteract this, apart from trying to reduce the decoherance rate of the qubit, much effort is put into devising quantum error correction codes: devise strategies such that potential errors can be detected and corrected for.
	For topological quantum computers, employing Majorana bound states as qubits, information is encoded in such a way that it is inherently protected against decoherence.
	This \emph{topological} protection of the quantum states makes Majorana bound states (MBSs) a promising candidate as a stable platform for quantum computing.
	However, the implementation of such Majorana bound states has proven elusive, and much research is being done on designing a device that reliably and unequivocally hosts Majoranas.
	In this manuscript, we devise a novel way to improve the reliability of such devices, while remaining compatible with current fabrication techniques.

@@

	\comment{What are Majorana bound states}
	Majorana particles are particles that always come in pairs: one pair of Majorana's forms a single electronic state.
	Disambiguating electrons and holes into their Majorana counterparts is analogous to splitting a complex number into its real and imaginary part.
	We write the Majorana operators in terms of the creation (annihilation) and annihilation (creation) operators of electrons (holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:

@@

\section{Ways to make Majorana's: nanowires \& sns system}
	A realistic experimental implementation of Kitaev's model did not emerge until the similar works of Lutchyn et. al~\cite{lutchyn_majorana_2010} and Oreg et. al~\cite{ oreg_helical_2010}, where they proposed an experiment composed of a semiconducting nanowire deposited onto a superconductor.
	They predicted that, if the semiconductor has strong spin-orbit coupling, a magnetic field applied along the wire axis, as well as a carefully tuned chemical potential, Majoranas would appear at the ends of the nanowire.
	The experiment proved to be sufficiently practical to perform in the lab and the first signatures of Majorana bound states were found using the setup by Mourik et. al~\cite{mourik_signatures_2012}.

@@

\section{Majoranas in a Josephson junction}
	\comment{Why are SNS junctions potentially better?}
	A more convincing case could be made if one could control the system in such a way that the presence of Majoranas can be turned on or off.
	This feature is realized in a relatively recent proposal by Pientka et. al~\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
	On each side of the strip a superconductor is placed, forming a Josephson junction.
	Using the Josephson junction, one can use the supercurrent which flows between the two superconductors to control whether the system is in a topological phase (meaning it contains Majoranas), or not.
	The system has addition advantages, namely the system allows for Majorana's to be created at lower magnetic fields, the system is more compatible with convential semiconductor technology, and the Josephson junction allows for new ways to detect the topological phase of the system.

>>>>

\comment{It is still an open question what the implementation for a qubit will be, but Majoranas are one of the contenders}
	If we consider the evolution of the regular computer, we see that the technological/physical platform for the bit, the binary unit of information, has been constantly changing.
	For the earliest computers, complex electromechanical systems with gears and cogs fulfilled this role.
	Soon after, binary states were implemented in the form of vacuum tubes, and nowadays it is the transistor which acts as the basic unit of computation.
	Similarly, because quantum computing is still in its infancy, there are still many contenders for what the underlying technology will be: what physical system will form the basis for the quantum bit, the qubit?
	The platforms which are currently explored for the implementation of a qubit include the transmon qubit~\cite{wendin_quantum_2017}, NV-centers~\cite{childress_diamond_2013}, quantum dots~\cite{kloeffel_prospects_2013}, and Majorana bound states~\cite{wendin_quantum_2017}.
	The main problem with most of the quantum computing platforms is that it is very difficult to keep the qubit from decohering.
	To counteract this, apart from trying to reduce the decoherance rate of the qubit, much effort is put into devising quantum error correction codes: devise strategies such that potential errors can be detected and corrected for.
	For topological quantum computers, employing Majorana bound states as qubits, information is encoded in such a way that it is inherently protected against decoherence.
	This \emph{topological} protection of the quantum states makes Majorana bound states (MBSs) a promising candidate as a stable platform for quantum computing.
	However, the implementation of such Majorana bound states has proven elusive, and much research is being done on designing a device that reliably and unequivocally hosts Majoranas.
	In this manuscript, we devise a novel way to improve the reliability of such devices, while remaining compatible with current fabrication techniques.

@@

	\comment{What are Majorana bound states}
	Majorana particles are particles that always come in pairs: one pair of Majoranas forms a single electronic state.
	Disambiguating electrons and holes into their Majorana counterparts is analogous to splitting a complex number into its real and imaginary part.
	We write the Majorana operators in terms of the creation (annihilation) and annihilation (creation) operators of electrons (holes), respectively $\hat{c}^\dagger$ and $\hat{c}$:

@@

\section{Ways to make Majoranas: nanowires \& sns system}
	A realistic experimental implementation of Kitaev's model did not emerge until the similar works of Lutchyn et. al~\cite{lutchyn_majorana_2010} and Oreg et. al~\cite{ oreg_helical_2010}, where they proposed an experiment composed of a semiconducting nanowire deposited onto a superconductor.
	They predicted that, if the semiconductor has strong spin-orbit coupling, a magnetic field applied along the wire axis, as well as a carefully tuned chemical potential, Majoranas would appear at the ends of the nanowire.
	The experiment proved to be sufficiently practical to perform in the lab and the first signatures of Majorana bound states were found using the setup by Mourik et. al~\cite{mourik_signatures_2012}.

@@

\section{Majoranas in a Josephson junction}
	\comment{Why are SNS junctions potentially better?}
	A more convincing case could be made if one could control the system in such a way that the presence of Majoranas can be turned on or off.
	This feature is realized in a relatively recent proposal by Pientka et. al~\cite{pientka_topological_2017}, where, instead of a nanowire, a two-dimensional strip of semiconductor is used.
	On each side of the strip a superconductor is placed, forming a Josephson junction.
	Using the Josephson junction, one can use the supercurrent which flows between the two superconductors to control whether the system is in a topological phase (meaning it contains Majoranas), or not.
	The system has addition advantages, namely the system allows for Majoranas to be created at lower magnetic fields, the system is more compatible with convential semiconductor technology, and the Josephson junction allows for new ways to detect the topological phase of the system.

### 2019-02-04 thesis_report/results.tex
Majorana's -> Majoranas

	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majorana's}
	\section{Increased isolation and stability of the Majorana state}

@@

		\comment{Introduction of a zigzag leads to localization of the Majorana's}
		\subsection{Majorana decay length}

@@

			\comment{In a straight system, the Majorana's are very poorly localized.}
			For the ribbon system, we see that the decay of the density is slow: the wavefunction clearly extends to the middle of the system, not showing the delocalization sought after.
			Apart from the density, as mentioned in the Theory chapter, overlap of Majorana's leads to a non-zero energy of the state.
			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majorana's are very poorly localized, and topological protection against perturbations is minimal.

			\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
			All of the zigzag type geometries show a greatly reduced coherence length.
			The delocalized nature of the wavefunctions is clearly visible through the density plots.
			Quantitatively, the improvement in localization of the Majorana's is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest lying wavefunctions.
			As mentioned in the previous section, this can be attributed due to the way the gap and velocity factor into the Majorana coherence length.

@@

		\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
		\subsection{Phase diagram}

>>>>

	\comment{Introduction of a zigzag opens up the gap, creates a more stable topological phase diagram, and decreases coherence length of Majoranas}
	\section{Increased isolation and stability of the Majorana state}

@@

		\comment{Introduction of a zigzag leads to localization of the Majoranas}
		\subsection{Majorana decay length}

@@

			\comment{In a straight system, the Majoranas are very poorly localized.}
			For the ribbon system, we see that the decay of the density is slow: the wavefunction clearly extends to the middle of the system, not showing the delocalization sought after.
			Apart from the density, as mentioned in the Theory chapter, overlap of Majoranas leads to a non-zero energy of the state.
			Taking this into consideration, we see that the energy of the Majorana state in the straight system is only barely below the next lowest lying eigenstate: the Majoranas are very poorly localized, and topological protection against perturbations is minimal.

			\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}
			All of the zigzag type geometries show a greatly reduced coherence length.
			The delocalized nature of the wavefunctions is clearly visible through the density plots.
			Quantitatively, the improvement in localization of the Majoranas is also distinctly apparent: the energies of the Majorana states are orders of magnitude lower than the energy of the second lowest lying wavefunctions.
			As mentioned in the previous section, this can be attributed due to the way the gap and velocity factor into the Majorana coherence length.

@@

		\comment{Zigzag Majoranas have a cleaner phase diagram due to the reduction in symmetry class}
		\subsection{Phase diagram}

### 2019-02-04 thesis_report/theory.tex
Majorana's -> Majoranas

\chapter{Theoretical Background}
The topological quantum computer uses pairs of Majorana particles as its unit of computation (qubit).
In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
As this material does not seem to exist on its own, one creates a heterogeneous system.
I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majorana's.

@@

	\subsection{Superconducting Hamiltonian}
		For the purpose of creating Majorana's, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
		We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
		This can be achieved by modeling superconductivity with the Boguliubov de Gennes Hamiltonian, which ensures particle-hole symmetry:

@@

	\subsection{Proximity effect}
		In order to create Majorana's, one needs a material with properties unique to both superconductors and semiconductors.
		However, if a superconductor is interfaced with a normal conductor, some of the properties belonging to the superconductor transfer to normal material.
		This effective transfer of properties to the normal material is known as the proximity effect.
		The characteristic distance governing the decay of the superconducting behavior is given by the superconducting coherence length, Eq.\eqref{eq:theory_sc_coherence_length}

@@

	Topology is relevant to the context of the system under study, because the emergence of seperated Majorana's is guaranteed within a continuous range of parameters.
	The presence of Majorana's is therefore topologically protected, as they will be unpurturbed by variations of parameters, within a certain range.
	For an infinite system, the system is said to be in the topological phase if Majorana's emerge once the system is cut to finite length.
	The system is considered to be in its trivial phase if the converse is true.
	The allocation of a system into one of its phases (in this case two) is quantitatively captured by its topological invariant.
	The relevant topological invariant is dependent on the symmetry class the system belongs to.
	In the case of the what is studied in this manuscript, the systems discussed belong to either symmetry class BDI or D.
	Any system which is in the BDI class is also contained within class D.
	The topological invariant of a class D system is binary: $-1$, corresponding to the topological phase, and $1$, corresponding to the trivial phase.
	The invariant of a BDI system can be any integer number, which also means there are more than two topological phases.
	More importantly, the transition of the system from one topological phase to the other means the system must undergo a gap closing.

@@

		The Majorana state is a superposition of electrons and holes, and is its own anti-particle: exchanging electrons and holes yields the same state.
		The Majorana state carries no spin, charge, or energy, giving almost no degrees of freedom for it to interact with the environment.
		The Majorana state constitutes a single fermion, but is comprised of two Majorana's.
		In a finite, topological system, these two Majorana's are physically seperated, appearing at the edges.

		The lack of interaction, as well as the physical seperation of the state, makes it very robust against perturbations, but also difficult to detect.
		Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
		When measuring the conduction through a system with Majorana's present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.

@@

	\subsection{Decay/Coherence length}
		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majorana's, diminishing the desired robustness of the state.
		An overlap of the Majorana's will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
		A crude estimation of the size of an individual Majorana is:
		\begin{equation}
			\xi = \hbar \frac{v_\text{F}}{\Delta_\text{topological}}
			\label{eq:majorana_coherence_length}
		\end{equation}

		When the system is cut to a finite length, any overlap of the two Majorana's will lead to a non-zero energy.
		This decreases the robustness of the topological state and it is thus desirable that the Majorana decay length is significantly smaller than the system size.

@@

	The earliest devices used to create a seperated pair of Majorana's were nanowires deposited onto a slab of superconducting material.
	A relatively new proposal is that of creating Majorana's in a planar Josephson junction~\cite{pientka_topological_2017}.
	An advantage of this system is that the phase difference between the superconductors can be used as a knob to switch the system from the topological state to the trivial state. 
	In addition, the presence of the second superconductor increases the topological gap of the system due to the proximity effect.

>>>>

\chapter{Theoretical Background}
The topological quantum computer uses pairs of Majorana particles as its unit of computation (qubit).
In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
As this material does not seem to exist on its own, one creates a heterogeneous system.
I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majoranas.

@@

	\subsection{Superconducting Hamiltonian}
		For the purpose of creating Majoranas, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
		We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
		This can be achieved by modeling superconductivity with the Boguliubov de Gennes Hamiltonian, which ensures particle-hole symmetry:

@@

	\subsection{Proximity effect}
		In order to create Majoranas, one needs a material with properties unique to both superconductors and semiconductors.
		However, if a superconductor is interfaced with a normal conductor, some of the properties belonging to the superconductor transfer to normal material.
		This effective transfer of properties to the normal material is known as the proximity effect.
		The characteristic distance governing the decay of the superconducting behavior is given by the superconducting coherence length, Eq.\eqref{eq:theory_sc_coherence_length}

@@

	Topology is relevant to the context of the system under study, because the emergence of seperated Majoranas is guaranteed within a continuous range of parameters.
	The presence of Majoranas is therefore topologically protected, as they will be unpurturbed by variations of parameters, within a certain range.
	For an infinite system, the system is said to be in the topological phase if Majoranas emerge once the system is cut to finite length.
	The system is considered to be in its trivial phase if the converse is true.
	The allocation of a system into one of its phases (in this case two) is quantitatively captured by its topological invariant.
	The relevant topological invariant is dependent on the symmetry class the system belongs to.
	In the case of the what is studied in this manuscript, the systems discussed belong to either symmetry class BDI or D.
	Any system which is in the BDI class is also contained within class D.
	The topological invariant of a class D system is binary: $-1$, corresponding to the topological phase, and $1$, corresponding to the trivial phase.
	The invariant of a BDI system can be any integer number, which also means there are more than two topological phases.
	More importantly, the transition of the system from one topological phase to the other means the system must undergo a gap closing.

@@

		The Majorana state is a superposition of electrons and holes, and is its own anti-particle: exchanging electrons and holes yields the same state.
		The Majorana state carries no spin, charge, or energy, giving almost no degrees of freedom for it to interact with the environment.
		The Majorana state constitutes a single fermion, but is comprised of two Majoranas.
		In a finite, topological system, these two Majoranas are physically seperated, appearing at the edges.

		The lack of interaction, as well as the physical seperation of the state, makes it very robust against perturbations, but also difficult to detect.
		Luckily, the state's presence itself is measurable: the availability of a state contributes to the conduction at that energy.
		When measuring the conduction through a system with Majoranas present, one should thus encounter a rise in the conductance at zero energy: the zero bias peak.

@@

	\subsection{Decay/Coherence length}
		The decay or coherence length of a Majorana pair is an important measure signifying the seperation of the two half-particles.
		A decay length larger or of equal size to the system dimensions will lead to overlap of the Majoranas, diminishing the desired robustness of the state.
		An overlap of the Majoranas will in fact lead to the system having a non-zero energy, its magnitude depending on the amount of overlap.
		A crude estimation of the size of an individual Majorana is:
		\begin{equation}
			\xi = \hbar \frac{v_\text{F}}{\Delta_\text{topological}}
			\label{eq:majorana_coherence_length}
		\end{equation}

		When the system is cut to a finite length, any overlap of the two Majoranas will lead to a non-zero energy.
		This decreases the robustness of the topological state and it is thus desirable that the Majorana decay length is significantly smaller than the system size.

@@

	The earliest devices used to create a seperated pair of Majoranas were nanowires deposited onto a slab of superconducting material.
	A relatively new proposal is that of creating Majoranas in a planar Josephson junction~\cite{pientka_topological_2017}.
	An advantage of this system is that the phase difference between the superconductors can be used as a knob to switch the system from the topological state to the trivial state. 
	In addition, the presence of the second superconductor increases the topological gap of the system due to the proximity effect.
